Inferring Continuous and Discrete Population Genetic Structure Across Space

### 2017-09-15 writeup/conStruct.tex

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}
\plr{WRITE AUTHOR SUMMARY}

>>>>

\newpage

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}
One of the first steps in the analysis of genetic data, 
and a principal mission of biology, 
is to describe and categorize natural variation. 
A continuous pattern of differentiation, 
such as when individuals found closer together in space 
are, on average, more genetically similar than individuals sampled farther apart, 
can confound attempts to categorize natural variation into discrete groups.  
This is because current statistical methods for assigning individuals to discrete clusters 
cannot accommodate continuous spatial patterns, 
making it seem as though there are many more clusters than there actually are. 
Such patterns are common in nature, 
so this shortcoming of existing methods may have widespread repercussions.
In this study, we introduce a new statistical method 
for categorizing natural genetic variation - 
one that describes variation as a combination of continuous and discrete patterns.
Using simulated data, we show how current approaches can be misleading, 
and also demonstrate that our new method works well.  
We predict that our method will be an important tool for the analysis of genetic data.
